%PREAMBLE
\documentclass{awesome-cv}
\usepackage{multicol, hyperref}
\usepackage[super]{nth}
\colorlet{awesome}{teal}

 % \definecolor{darktext}{HTML}{00FF00} %green
 % \definecolor{text}{HTML}{FF00FF} % pink
% \definecolor{graytext}{HTML}{FF0000} % red
 % \definecolor{lighttext}{HTML}{0000FF} %blue

%\RequirePackage{fontawesome}
%\setlist{nosep}

%PERSONAL INFORMATION (this will be included in the header)
\name{Bradley}{Boxer}
\position{Software Engineering Student}
\mobile{(908) 300-2095}
\email{brad.boxer1@gmail.com}
\github{Bradley-B}

\begin{document}
	\makecvheader[C]

	\makecvfooter
		{\today}
		{Bradley Boxer~~~~.~~~~R\'esum\'e}
		{}

	%EDUCATION
	\cvsection{EDUCATION}
		\begin{cventries}
			\cventry
				{Bachelor of Science in Software Engineering}
				{Rochester Institute of Technology}
				{Rochester, New York}
				{2018 - 2023}
                {\textbf{GPA: 3.90} \nth{2} Year}
		\end{cventries}

	%PROJECTS
	\cvsection{PROJECTS}
		\begin{cventries}
			\cventry
				{\href{https://github.com/Bradley-B/ScavengerHuntAndroid}{https://github.com/Bradley-B/ScavengerHuntAndroid}}
				{Scavenger Hunt}
				{May 2018 - Present}
				{}
				{Solo project. Android app. Create and share real-world scavenger hunts using GPS coordinates and QR codes. Uses a Firebase Cloud Store database to store user data. Written in Java and currently on the Google Play Store.}

			\cventry
				{Code Available Upon Request}
				{WebCheckers}
				{January - May 2019}
				{}
				{Group project. An online Checkers game system built in Java 8 and Spark, a web micro-framework. Supports multiple consecutive users, spectating games, and an AI opponent. Created as part of the Introduction to Software Engineering course at RIT.}

            		\cventry
                		{\href{https://github.com/Bradley-B/Flask-Experiments}{https://github.com/Bradley-B/Flask-Experiments}}
                		{Personal Website}
                		{February 2019 - Present}
                		{}
                		{Solo project. Code for my personal website \href{http://bradleyboxer.com}. Written in Python using Flask.}

		\end{cventries}
	%WORK EXPERIENCE
	\cvsection{WORK EXPERIENCE}
		\begin{cventries}
			\cventry
				{Hospitality Worker}
				{HomePlate Catering}
				{Bridgewater, New Jersey}
               			{\textbf{May-August, 2017-2019}}
				{Concessions/Kitchen worker. Practiced essential communication skills such as teamwork and customer diplomacy as well as working quickly and efficiently in a high-pressure environment.}
		\end{cventries}

	
	\vspace{0.5cm}
	%2 Column Section
	\begin{multicols}{2}

		%SKILLS
		\cvsection{SKILLS}\\
			\\\textbf{\textit{LANGUAGES}}
			\begin{itemize}[nosep]

				%Languages that I am proficient in
				\item \textbf{PROFICIENT}
					\begin{itemize}[nosep]
					\item Java
					\item Python	
				\end{itemize}

				%Languages that I am familiar with
				\item \textbf{ACTIVELY LEARNING}
					\begin{itemize}[nosep]
					\item C
					\item Ruby
					\item Bash
					\item SQL
					\item HTML/CSS
					\item JavaScript	
					\item \LaTeX
				\end{itemize}
			\end{itemize}
				
			\textbf{\textit{PROGRAMS / ENVIRONMENTS}}
			\begin{itemize}[nosep]
				\item Android Studio
				\item GNU/Linux and Unix-like systems
				\item Vim
				\item Jetbrains products
			\end{itemize}
		\columnbreak
		\cvsection{EXTRACURRICULAR}
			\vspace*{-.25cm}
			\begin{cvhonors}
			        \cvhonor{General Member}{Society of Software Engineers}{}{2019}
                		\cvhonor{Captain}{FIRST Robotics Competition Team 303}{}{2017-2018}
			\end{cvhonors}
			\vspace*{-.25cm}
		\cvsection{COURSES}
			\vspace*{-.25cm}
			\begin{cvhonors}
				\cvhonor{CSAPX}{RIT}{}{2018}
				\cvhonor{Personal Software Engineering}{RIT}{}{2019}
				\cvhonor{Introduction to Software Engineering}{RIT}{}{2019}
				\cvhonor{Engineering of Software Subsystems}{RIT}{}{2019}
				\cvhonor{Math Models of Software}{RIT}{}{2019}
			\end{cvhonors}
			\vspace*{-.25cm}

%		\cvsection{VOLUNTEERING}
%			\vspace*{-.25cm}
%			\begin{cvhonors}
%				\cvhonor{Cameraman/Editor}{Newtown Board of Ed}{}{2014-2017}
%				\cvhonor{Video Creator}{Relay for Life}{}{2014}
%			\end{cvhonors}
	\end{multicols}	
	\vspace*{-.5cm}
%	\cvsection{HONORS}
%		\begin{cvhonors}
%			\cvhonor{Honors Program}{Rochester Institute of Technology}{}{2017-2018}
%			\cvhonor{Presidential Scholarship}{Rochester Institute of Technology}{}{2017}
%			\cvhonor{RIT Computing Medal}{Rochester Institute of Technology}{}{2016}
%			\cvhonor{National Honor Society}{Newtown High School}{}{2015-2017}
%			\cvhonor{National Latin Award, Summa Cum Laude}{American Classical League}{}{2014-2017}
%		\end{cvhonors}
\end{document}
